02_limma_hyp

### 2019-03-19 scripts/02_limma_hyp.Rmd
now with a function

# female comparisons
cont <- "FH_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_CB', frame.plot=F)

cont <- "FH_BL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_BL', frame.plot=F)

cont <- "FH_Li3"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_Li3', frame.plot=F)

cont <- "FH_i39"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_i39', frame.plot=F)

cont <- "FH_i917"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_i917', frame.plot=F)

cont <- "FH_i17H"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_i17H', frame.plot=F)

cont <- "FH_H5"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_H5', frame.plot=F)

cont <- "FH_n59"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_n59', frame.plot=F)

cont <- "FH_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_n9C', frame.plot=F)

## male comparisons

cont <- "MH_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_CB', frame.plot=F)

cont <- "MH_BL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_BL', frame.plot=F)

cont <- "MH_Li3"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_Li3', frame.plot=F)

cont <- "MH_i39"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_i39', frame.plot=F)

cont <- "MH_i917"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_i917', frame.plot=F)

cont <- "MH_i17H"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_i17H', frame.plot=F)

cont <- "MH_H5"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_H5', frame.plot=F)

cont <- "MH_n59"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_n59', frame.plot=F)

cont <- "MH_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_n9C', frame.plot=F)

## nesting to building

cont <- "FH_n9B"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_n9B', frame.plot=F)

cont <- "MH_n9B"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_n9B', frame.plot=F)

>>>>

mycontrasts <- c("FH_CB", "FH_BL", "FH_Li3", "FH_i39", "FH_i917", "FH_i17H", "FH_H5", "FH_n59", "FH_n9C",
                 "MH_CB", "MH_BL", "MH_Li3", "MH_i39", "MH_i917", "MH_i17H", "MH_H5", "MH_n59", "MH_n9C",
                 "FH_n9B", "MH_n9B")

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
  print(kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1))
  print(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}

for(i in mycontrasts){
  printplotcontrasts(i)
}
